Multi-level Selective Deduplication for VM Snapshots in Cloud Storage

### 2012-03-01 vm_snapshot_sim/2012arch.tex
tao

\subsection{Snapshot Service Architecture}
%\subsection{Aliyun's VM Cloud and 
Our architecture is built on the Aliyun platform which provides the largest public VM cloud in China 
based on Xen~\cite{Xen2003}. A typical VM cluster in our cloud environment
consists of from hundreds to thousands of physical machines, each of which can
host tens of VMs. A few varieties of mainstream OS are supported,
including several editions of Windows Server, major Linux distributions, and FreeBSD.
During the VM creation, a user chooses her flavor of OS distribution and the cloud system 
copies the corresponding pre-configured base VM image to her VM as the OS disk, 
and an empty data disk is created and mounted onto her VM as well. 
All these virtual disks are represented as virtual machine image files in our
underline runtime VM storage system. The runtime I/O between virtual machine and its virtual
disks is tunneled by the virtual device driver (called TapDisk at Xen). To avoid network latency and congestion, 
Aliyun's distributed file system carefully selects the location of primary replica of VM's 
image files such that they are located on the same physical machine of VM instance.

@@

With Aliyun's distributed file system support, the snapshot store operates a few \emph{append-only} files
in the underline file storage. Each virtual disk has its own data store, all data 
blocks after deduplication will be stored into that system.
Since all the underline data structures is append only,
upon a delete request, the corresponding data will only be marked rather than being deleted.
A compaction will take place when deleted data has accumulated to a certain threshold, thus 
reclaiming the disk space .

@@

At the runtime, the CDS index resides in a distributed  memory lookup table  
implemented using Memcached~\cite{memcached} to leverage the aggregated memory in a cluster.
Th usage of memory at each machine is small and thus  this scheme  does not
lead to  a memory resource contention with the existing cloud services.
For example, in our current implementation setting at Aliyun, we use up to  150MB memory per node during night backup
including CDS and other metadata for all levels of deduplication. Most of memory resource (48GB per node 
in our experiment) is used for existing  applications.
Each CDS content data stored  in the distributed file system
has multiple copies in different machines for the purpose of fault tolerance and 
while providing high read  throughput.  
%The data of CDS is stored in a special block store in the distribued file system.

@@

In Aliyun's VM cloud, each VM explicitly maintains  one OS disk, plus  one or more data disks.
During VM's creation, its OS disk is directly copied from user's chosen base image.
Given the separation of OS disks and data disks, we study  their characteristics separately.
We expect that the operating system and along with popular software installations  are not frequently
modified or deleted. 
%base image data as a hint.Through users may change configurations, install software, or write user data into OS disk,
%Thus most of content blocks for the OS related snapshots  shall keep unchanged.
%This is verified in  Section~\ref{sect:exper}.
We have sampled  the  popularity of common blocks in the OS and data disks from a dataset
containing over 1,000 VMs and each has 10 snapshots.
Figure \ref{fig:zipf-data} shows the duplicate count  for different data blocks sorted by their ranking in 
terms of the duplication count. $Y$ axis is the popularity of a data block in a log scale 
measured its duplicate count among snapshots. $X$ axis is the identification of data blocks in a log scale
sorted by their duplicate rank.  The rank number  1  is the block with the highest number of duplicates.
The curve exhibits that the popularity of common data blocks partially follows a  Zipf-like distribution.

\begin{figure}[htbp]
\centering
%\epsfig{file=images/log-log.disk.eps, height=2in, width=2.66in}
%\epsfig{file=images/log-log.disk.eps, width=3in}
\epsfig{file=images/datadisk.count_rank.eps, width=3in}
\caption{Duplicate count  of common data blocks in a log scale.}
\label{fig:zipf-data}
\end{figure}
Figure \ref{fig:OSpopular} shows the duplicate count  for OS disk snapshot blocks sorted by their ranking.
$Y$ axis is the popularity of an OS block in a log scale 
measured its duplicate count among snapshots. $X$ axis is the identification of OS blocks in a log scale
sorted by their duplicate rank.  For the top ranked blocks, there is a flat line in terms of duplicate counts. That
is because there are a large number of OS blocks which have appeared in all copies of such OS releases.

\begin{figure}
\centering
%\epsfig{file=images/log-log.35vmos.eps,  width=3in}
%\epsfig{file=images/35os.count_rank.eps, width=3in}
\epsfig{file=images/35vmos.count-rank.eps,width=3in}
\caption{ Duplicate count of  common OS blocks in a log scale.}
\label{fig:OSpopular}
\end{figure}

>>>>

\subsection{Snapshot Service Architecture}
%\subsection{Aliyun's VM Cloud and 
Our architecture is built on the Aliyun platform which provides the largest public VM cloud in China 
based on Xen~\cite{Xen2003}. A typical VM cluster in our cloud environment
consists of from hundreds to thousands of physical machines, each of which can
host tens of VMs. A few varieties of mainstream OS are supported.
%including several editions of Windows Server, major Linux distributions, and FreeBSD.
During the VM creation, a user chooses her flavor of OS distribution and the cloud system 
copies the corresponding pre-configured base VM image to her VM as the OS disk, 
and an empty data disk is created and mounted onto her VM as well. 
All these virtual disks are represented as virtual machine image files in our
underline runtime VM storage system. The runtime I/O between virtual machine and its virtual
disks is tunneled by the virtual device driver (called TapDisk at Xen). To avoid network latency and congestion, 
Aliyun's distributed file system carefully selects the location of primary replica of VM's 
image files such that they are located on the same physical machine of VM instance.
During snapshot backup, concurrent disk write is logged 
so that each snapshot can have a   consistent version.

@@

With Aliyun's distributed file system support, the snapshot store operates 
\emph{append-only} files. Each virtual disk has its own data store, all data 
blocks after deduplication will be stored into that system.
Since all the underline data structures is append only,
upon a delete request, the corresponding data will only be marked rather than being deleted.
A compaction will take place when deleted data has accumulated to a certain threshold, thus 
reclaiming the disk space .

@@

At the runtime, the CDS index resides in a distributed  memory lookup table  
implemented using Memcached~\cite{memcached} to leverage the aggregated memory in a cluster.
Th usage of memory at each machine is small and thus  this scheme  does not
lead to  a memory resource contention with the existing cloud services.
%For example, in our current implementation setting at Aliyun, we use up to  150MB memory per node during night backup
%including CDS and other metadata for all levels of deduplication. Most of memory resource (48GB per node 
%in our experiment) is used for existing  applications.
CDS raw data stored  in the distributed file system
has multiple copies in different machines for the purpose of fault tolerance and 
while providing high read  throughput.  
%The data of CDS is stored in a special block store in the distribued file system.

@@

In Aliyun's VM cloud, each VM explicitly maintains  one OS disk, plus  one or more data disks.
During VM's creation, its OS disk is directly copied from user's chosen base image.
Given the separation of OS disks and data disks, we study  their characteristics separately.
We expect that the operating system and along with popular software installations  are not frequently
modified or deleted. 
%base image data as a hint.Through users may change configurations, install software, or write user data into OS disk,
%Thus most of content blocks for the OS related snapshots  shall keep unchanged.
%This is verified in  Section~\ref{sect:exper}.
We have sampled  the  popularity of common blocks in the OS and data disks from a dataset
containing over 1,000 VMs and each has 10 snapshots.

The left part of Figure \ref{fig:zipf-data} shows the duplicate count  for different data blocks sorted by their ranking in 
terms of the duplication count. $Y$ axis is the popularity of a data block in a log scale 
measured its duplicate count among snapshots. $X$ axis is the identification of data blocks in a log scale
sorted by their duplicate rank.  The rank number  1  is the block with the highest number of duplicates.
The curve exhibits that the popularity of common data blocks partially follows a  Zipf-like distribution.
The right part of Figure \ref{fig:zipf-data} shows the duplicate count  for OS disk snapshot blocks sorted by their ranking.
%$Y$ axis is the popularity of an OS block in a log scale 
%measured its duplicate count among snapshots. $X$ axis is the identification of OS blocks in a log scale
%sorted by their duplicate rank.  
For the top ranked blocks, there is a flat line in terms of duplicate counts. That
is because there are a large number of OS blocks which have appeared in all copies of such OS releases.

\begin{figure}[htbp]
\centering
%\epsfig{file=images/log-log.disk.eps, height=2in, width=2.66in}
%\epsfig{file=images/log-log.disk.eps, width=3in}

\begin{tabular}{cc}
\epsfig{file=images/datadisk.count_rank.eps, width=1.5in} &
\epsfig{file=images/35vmos.count-rank.eps,width=1.5in}
\end{tabular}

\caption{Duplicate count  of common data blocks in a log scale on the left. The right is for common OS blocks.}
\label{fig:zipf-data}
\end{figure}

%\begin{figure}
%\centering
%\epsfig{file=images/35vmos.count-rank.eps,width=3in}
%\caption{ Duplicate count of  common OS blocks in a log scale.}
%\label{fig:OSpopular}
%\end{figure}

### 2012-03-01 vm_snapshot_sim/main.tex
tao

\documentclass[finalversion]{usetex-v1}
%\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{epsfig}
%\usepackage{breakurl}
%% Define a new 'leo' style for the package that will use a smaller font.
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
\makeatother
%% Now actually use the newly defined style.
\urlstyle{leo}
%\linespread{1.2}
%\setlength{\parskip}{1ex}
\begin{document}
\title{Data Deduplication and Zipf-like Distribution in VM Cloud Storage}
\author{Wei Zhang, Hong Tang, Hao Jiang, Rachael Zeng, Xiaogang Li, Tao Yang}
\date{}
\maketitle

\input{abstract}
\input{intro} %introduce the problem, related solutions and our requirements
\input{cds} %data study, zipf, model of cds size and dedup efficiency
\input{approach} %our dedup process
\input{results}
%\input{related}
%\input{future}
\input{conclusion}
\bibliographystyle{abbrv}
\bibliography{dedup}
\end{document}

>>>>

\documentclass[finalversion]{usetex-v1}
%\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{epsfig}
%\usepackage{breakurl}
%% Define a new 'leo' style for the package that will use a smaller font.
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
\makeatother
%% Now actually use the newly defined style.
\urlstyle{leo}
%\linespread{1.2}
%\setlength{\parskip}{1ex}

\newcommand{\comments}[1]{}

\begin{document}
%\title{Selective Deduplication for VM Snapshots in Cloud Storage}
\title{Multi-level Selective Deduplication for VM Snapshots in Cloud Storage}
%\title{Data Deduplication and Zipf-like Distribution in VM Cloud Storage}
\author{Wei Zhang$^{\star\dagger}$, Hong Tang$^\dagger$, Hao Jiang$^\dagger$, Tao Yang$^\star$, 
Xiaogang Li$^\dagger$, and Rachael Zeng$^\dagger$ \\
   {\normalsize $^\star$UC Santa Barbara}\\
   {\normalsize$^\dagger$Alibaba.com}
}

\date{}
\maketitle

%need to explain: vm cloud, vm backup, dedup fundamentals, vm dedup(2 works), distributed dedup, zipf
%need to define: requirements, design considerations, architecture

\input{2012abs}
\input{2012intro} %introduce the vm cloud, backup problem, and our requirements
\input{2012background} %related works, related solutions, 
\input{2012arch} %, design considerations, architecture
\input{2012eval} %data study, zipf, model of cds size and dedup efficiency
%\input{results}
%\input{related}
%\input{future}
\input{2012concl}

      %\setlength{\itemsep}{ex}%
%      \setlength{\parskip}{0ex}%
%\setlength{\itemsep}{-3mm}

	%\linespread{0.3} 
  \let\oldthebibliography=\thebibliography
  \let\endoldthebibliography=\endthebibliography
  \renewenvironment{thebibliography}[1]{%
    \begin{oldthebibliography}{#1}%
      \setlength{\parskip}{-0.02ex}%
      \setlength{\itemsep}{-0.02ex}%
      \setlength{\baselineskip}{-0.02ex}%

  }%
  {%
    \end{oldthebibliography}%
  }
{\small
\bibliographystyle{abbrv}
\bibliography{dedup,dedup1}
}
\end{document}
